No Replication Without Process Documentation:  An Assessment of Management

### 2020-04-23 R/MSE-manuscript.Rmd
Fix strsplit split value that I broke AGAIN, ugh!

part.data_pub<- part.data_pub %>%
    purrr::map(~ strsplit(as.character(.),split=", ")) %>%
    purrr::map(unlist) %>%
    purrr::map(table)

@@

part.data_CC<- part.data_CC %>%
  purrr::map(~ strsplit(as.character(.),split=", ")) %>%
  purrr::map(unlist) %>%
  purrr::map(table)

@@

# What drivers are considered
drive.data_pub<-data_pub %>%
    select(Drivers) %>%
    purrr::map(~ strsplit(as.character(.),split=", ")) %>%
    purrr::map(unlist) %>%
    purrr::map(table) %>%
    plyr::ldply(data.frame) %>%
    select(Var1,Freq) %>%
    rename("Driver"="Var1","Frequency"="Freq") %>%
    mutate(Percent=Frequency/n_pub*100) %>%
    arrange(desc(Frequency))

drive.data_CC<-data_CC %>%
  select(Drivers) %>%
  purrr::map(~ strsplit(as.character(.),split=", ")) %>%
  purrr::map(unlist) %>%
  purrr::map(table) %>%
  plyr::ldply(data.frame) %>%
  select(Var1,Freq) %>%
  rename("Driver"="Var1","Frequency"="Freq") %>%
  mutate(Percent=Frequency/n_CC*100) %>%
  arrange(desc(Frequency))

>>>>

part.data_pub<- part.data_pub %>%
    purrr::map(~ strsplit(as.character(.),split=";")) %>%
    purrr::map(unlist) %>%
    purrr::map(table)

@@

part.data_CC<- part.data_CC %>%
  purrr::map(~ strsplit(as.character(.),split=";")) %>%
  purrr::map(unlist) %>%
  purrr::map(table)

@@

# What drivers are considered
drive.data_pub<-data_pub %>%
    select(Drivers) %>%
    purrr::map(~ strsplit(as.character(.),split=";")) %>%
    purrr::map(unlist) %>%
    purrr::map(table) %>%
    plyr::ldply(data.frame) %>%
    select(Var1,Freq) %>%
    rename("Driver"="Var1","Frequency"="Freq") %>%
    mutate(Percent=Frequency/n_pub*100) %>%
    arrange(desc(Frequency))

drive.data_CC<-data_CC %>%
  select(Drivers) %>%
  purrr::map(~ strsplit(as.character(.),split=";")) %>%
  purrr::map(unlist) %>%
  purrr::map(table) %>%
  plyr::ldply(data.frame) %>%
  select(Var1,Freq) %>%
  rename("Driver"="Var1","Frequency"="Freq") %>%
  mutate(Percent=Frequency/n_CC*100) %>%
  arrange(desc(Frequency))
